---
title: "Peer Graded Assignment for Motor Trend"
author: "Dipali Bagad"
date: "September 3, 2017"
output:
  pdf_document: default
  html_document: default
---
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Executive Summary

You work for Motor Trend, a magazine about the automobile industry. Looking at a data set of a collection of cars, they are interested in exploring the relationship between a set of variables and miles per gallon (MPG) (outcome). They are particularly interested in the following two questions:
1. Is an automatic or manual transmission better for MPG
2. Quantify the MPG difference between automatic and manual transmissions

## Data Processing
For analysis, first we need to load the dataset
```{r , echo=TRUE}
library(datasets)
data(mtcars)
# transform variables to factor format 
mtcars$am[mtcars$am==0]<-"Automatic"
mtcars$am[mtcars$am==1]<-"Manual"
mtcars$am<-as.factor(mtcars$am)
mtcars$cyl<-as.factor(mtcars$cyl)
mtcars$vs<-as.factor(mtcars$vs)
mtcars$gear<-as.factor(mtcars$gear)
mtcars$carb<-as.factor(mtcars$carb)
#read few records
head(mtcars)
#draw boxplot for transmission type comparision
boxplot(mtcars$mpg~as.factor(mtcars$am),col="green",ylab="MIles per Gallon",xlab="Transmission Type",main="MPG vs AM")
```

From graph we can say that manual transmissions have better mpg ratio than automatic transmissions. we can test this using welch test
```{r , echo=TRUE}
t.test(mpg~am,mtcars,paired=FALSE,var.equal=FALSE)
```

The p-value is less than 0.05, so this confirms the hypothesis.
we need to set basic and full model with possible variable and check which model influences more using step function and backward direction
```{r , echo=TRUE}
basic<-lm(mpg~am,mtcars)
full<-lm(mpg~.,mtcars)
fit<-step(full, direction="backward")
```

By Anova comparison we can see that very low f value. , we can say that its good to use the fit model instead of basic. The adjusted R squared is also much better (0.84 fit vs 0.34 basic)
```{r , echo=TRUE}
anova(basic,fit)
par(mfrow=c(1, 1))
plot(fit)
```

Residuals vs Fitted and Scale-Location plots show no pattern, the Normal Q-Q plot indicates that Residuals approximately follow a Normal distributions, and the Residuals vs Leverage plot tells that there's none particular outlier to be concerned.

## Conclusion
Based on analysis, we can conclude that manual transmissions are better than automatic by 1.80921 mpg. This is the diffence between the intercept of the fit model and Manual.