---
title: "Inferential Data Analysis Part2"
author: "Amol Nankar"
date: "November 22, 2016"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview of ToothGrowth data analysis

we're going to analyze the ToothGrowth data in the R datasets package.

1. Load the ToothGrowth data and perform some basic exploratory data analyses
2. Provide a basic summary of the data.
3. Use confidence intervals and/or hypothesis tests to compare tooth growth by supp and dose. (Only use the techniques from class, even if there's other approaches worth considering)
4. State your conclusions and the assumptions needed for your conclusions.



```{r ToothGrowth, echo=TRUE}
library(datasets)
library(ggplot2)

##1. Load the ToothGrowth data
data(ToothGrowth)


##2. Provide a basic summary of the data
summary(ToothGrowth)

dim(ToothGrowth)

head(ToothGrowth)

##Use confidence intervals and/or hypothesis tests to compare tooth growth by supp and dose.
ggplot(data=ToothGrowth, aes(x = factor(supp), y = len)) + geom_boxplot(aes(fill=factor(dose)))


ggplot(ToothGrowth, aes(x = factor(supp), y = len, fill = factor(supp))) + geom_violin(col = "yellow", size = 1) +
              geom_violin(aes(fill = factor(dose)))

## interval test to see if supplement has an impact on length. Group1 has data for VC and Group2 has lentth for OJ
## tooth growth by supplement type

supp_vc=ToothGrowth$len[ToothGrowth$supp=="VC"]
supp_oj=ToothGrowth$len[ToothGrowth$supp=="OJ"]
res<-t.test(supp_vc,supp_oj,var.equal = F,paired=F)
res$conf.int

##  interval test to see if Supplement VC with 2.0 does yields longer teeth. 

supp_vc20=ToothGrowth$len[ToothGrowth$supp=="VC" & ToothGrowth$dose==2.0]
supp_rest=ToothGrowth$len[!(ToothGrowth$supp=="VC" & ToothGrowth$dose==1.0)]
res<-t.test(supp_vc20,supp_rest,var.equal = F,paired=F)
res$conf.int


```

##Conclusion
1. Doses Supplement VC at 2.0 result in longer teeth
2. Supplement does not have a significant impact

